### 2014-11-13 tex/intro.tex
tweak to the intro

The goal of this work is to mitigate the state space explosion problem
in GSE by grouping multiple heaps together and only partitioning the
heaps at points of divergence in the control flow graph. Our
inspiration is found in the domain of static analysis that uses sets
of constraints over heap locations to encode multiple heaps in a
single representation. These sets, sometimes known as \emph{value sets} or
\emph{value summaries}, allow multiple heaps to be represented simultaneously
with a higher degree of precision than afforded by traditional
techniques for shape analysis.

Some of these
previous attempts, however, are unable to handle aliasing in heaps due
to a recursive definition of objects~\cite{..}, while others require a
set of heaps as input and are unable to initialize heaps
on-the-fly~\cite{..}. For these reasons the techniques use
over-approximations to reason about heaps and may report false
positives. Also, update to heaps require a rewrite of the constraint
system making it prohitive for use in the context of symbolic
execution.

>>>>

The goal of this work is to mitigate the state space explosion problem
in GSE by grouping multiple heaps together and only partitioning the
heaps at points of divergence in the control flow graph. Our
inspiration is found in the domain of static analysis that uses sets
of constraints over heap locations to encode multiple heaps in a
single representation. These sets, sometimes known as \emph{value
  sets} or \emph{value summaries}, allow multiple heaps to be
represented simultaneously with a higher degree of precision than
afforded by traditional techniques for shape analysis. Some of these
previous attempts, however, are unable to handle aliasing in heaps due
to a recursive definition of objects~\cite{..}, while others require a
set of heaps as input and are unable to initialize heaps
on-the-fly~\cite{..}.  As is typical in static analysis, over
approximation of the heap representations alleviates some of the
limitations but also leads to false positives. Also, update to heaps
require a rewrite of the constraint system making it prohitive for use
in the context of symbolic execution.
